\newpage
\thispagestyle{empty}  % No header/footer on this page

\begin{center}
    \textbf{UNIVERSITY SCHOOL OF INFORMATION AND\\ 
    COMMUNICATION TECHNOLOGY}\\
    \textbf{GAUTAM BUDDHA UNIVERSITY}\\
    \textbf{GREATER NOIDA-201312, UTTAR PRADESH, INDIA}\\
    \textbf{JUNE, 2025}\\
\end{center}
\vspace{1cm}
\begin{center}
    \textbf{\large CANDIDATE DECLARATION}
\end{center}

\vspace{0.5cm}

I hereby certify that the work embodied in this dissertation entitled 
\textbf{“REAL-TIME FACIAL EXPRESSION DETECTION USING CONVOLUTION NEURAL NETWORK”}, 
by \textbf{Abhishek Raj}, Roll No. \textbf{17/IEC/003} in partial fulfillment of the requirement for the award of the degree of 
\textbf{Integrated Dual Degree (B.Tech-M.Tech)} with specialization in 
\textbf{Artificial Intelligence and Robotics} submitted to the Department of CSE, 
University School of Information and Communication Technology, 
Gautam Buddha University, Greater Noida, is an authentic record of my own work carried out under the supervision of 
\textbf{Dr. Arun Solanki}. 
The matter presented in this dissertation has not been submitted by anyone in any other university/institute for the award of any other degree or diploma. 
Responsibility for any plagiarism-related issue stands solely with me.

\vspace{1.5cm}

\noindent
\textbf{Signature of the Student} \hfill \textbf{Abhishek Raj}  % Left & Right aligned

\vspace{1.5cm}

This is to certify that the above statement made by the candidate is correct to the best of my knowledge and belief. 
However, responsibility for any plagiarism-related issue solely stands with the student.

\vspace{1.5cm}

\noindent
\textbf{Dr. Arun Solanki} \hfill \textbf{Signature of the Supervisor}\\
Assistant Professor\\
Department of Computer Science and Engineering\\
University School of ICT,\\
Gautam Buddha University.\\

\vspace{1.5cm}

\noindent
\textbf{Mr. Panchanan Payare Singh} \hfill \textbf{Signature of the Co-Supervisor}

\vspace{1.5cm}

\noindent
\textbf{Date:} \underline{\hspace{3cm}} \hfill \textbf{Place:} Greater Noida, India.


